Injrury Outcomes - WHW matrices

### 2020-08-11 injury_tables.Rmd
Use first element of io to populate names of whw

scen_names_w_baseline <- c('bl', 'w_sc', 'bi_sc', 'car_sc', 'mc_sc', 'bus_sc')
scen_lt <- data.frame("scen_name" = names(io$accra$outcomes$whw), "val" = scen_names_w_baseline, stringsAsFactors = FALSE)

@@

    for (cs in names(io$accra$outcomes$whw)){

>>>>

scen_names_w_baseline <- c('bl', 'w_sc', 'bi_sc', 'car_sc', 'mc_sc', 'bus_sc')
scen_lt <- data.frame("scen_name" = names(io[[1]]$outcomes$whw), "val" = scen_names_w_baseline, stringsAsFactors = FALSE)

@@

    for (cs in names(io[[1]]$outcomes$whw)){
